### 2018-10-28 Sections/economics_of_the_quantum_internet.tex
minor

\dropcap{T}{he} computational leverage phenomena clearly implies that as the global quantum network expands over time, so too does the computational payback on investment into network expansion, or equivalently, the cost per unit of additional classical-equivalent processing time decreases exponentially.

@@

\begin{definition}[Static computational return]\index{Static computational return} The static computational return is the classical-equivalent processing power of a user's time-share, where the user has a fixed investment of one qubit, whereas the network is allowed to expand over time arbitrarily (e.g according to a quantum Moore's Law),
\begin{align}
	r_\mathrm{static}(t) &= \frac{f_\mathrm{sc}(N_t)}{N_t}\nonumber\\
	&= \chi_\mathrm{sc}(N_t),
\end{align}
which is equivalent to the collective per-qubit computational power of the entire network.
\end{definition}

Graphical examples for this relationship are equivalent to those presented earlier in Fig.~\ref{fig:NPSF}.

>>>>

\dropcap{T}{he} computational leverage phenomena clearly implies that as the global quantum network expands over time, so too does the computational payback on investment into network expansion, or equivalently, the cost per unit of additional classical-equivalent processing time decreases.

@@

\begin{definition}[Static computational return]\index{Static computational return} The static computational return is the classical-equivalent processing power of a user's time-share proportion, \mbox{$1/N_t$}, where the user has a fixed investment of one qubit, whereas the network is allowed to expand over time arbitrarily as $N_t$ (e.g according to a quantum Moore's Law),
\begin{align}
	r_\mathrm{static}(t) &= \frac{f_\mathrm{sc}(N_t)}{N_t}\nonumber\\
	&= \chi_\mathrm{sc}(N_t),
\end{align}
which is equivalent to the collective per-qubit computational power\index{Per-qubit computational power} of the entire network.
\end{definition}

Graphical examples for this relationship are equivalent to those presented earlier in Fig.~\ref{fig:NPSF}. In particular, for linear classical scaling functions the return is constant, whereas for exponential quantum scaling functions the return is exponential in network size.
